25 years of Social Work Research

### 2015-02-23 dataCleaning.Rmd
Code clean up.

full.df$record <- ifelse(full.df$record ==
    "Aretê",                                   #Spelling difference
      "Arete",
              full.df$record)

@@

full.df$record <- ifelse(full.df$record ==
    "Canadian Social Work Review/Revue canadienne de service social",
        "Canadian Social Work Review",
                        full.df$record)
```

>>>>

full.df$record <- ifelse(full.df$record ==
    "Aretê^",                                   #Spelling difference
      "Arete",
              full.df$record)

@@

full.df$record <- ifelse(full.df$record ==
    "Canadian Social Work Review/Revue canadienne de service social",
        "Canadian Social Work Review",
                        full.df$record)

full.df$record <- ifelse(full.df$record ==
    "INDIAN JOURNAL OF SOCIAL WORK",
        "Indian Journal of Social Work",
                      full.df$record)

full.df$record <- ifelse(full.df$record ==
    "The Indian Journal of Social Work",
        "Indian Journal of Social Work",
                            full.df$record)
